The Astropy Project

### 2017-11-13 main.tex
conclusion

\section{Outlook}
\label{sec:outlook}
\inlinecomment{hamogu}{This may be merged into the section above once
  that is fleshed out a little more.}  As shown above the development
of the \astropypkg package is making good progress, helping
astronomers worldwide to perform many daily tasks such as planning
observations, analyzing data or simulation results, and writing
publications. The strong emphasis that the \astropy project puts on
reliability and code correctness helps users to trust the calculations
performed with \astropypkg and to publish reproducible results. More
functionality is added to the core package and more and more
affiliated packages support more specialized needs.

At the same time, \astropy is spreading awareness of best practices in
software development. This is important since most practicing
astronomers received their education without being taught in computer
science and software development although a major fraction of almost
every astronomer's workload today is related to software use and
development. The \astropypkg package leads by example, showing all interested
astronomers how modern tools like git version control or continuous
integration (code is tested after every change to the source) can
increase the quality and accessibility of astronomical software
without overly complicating the development cycle. All submitted code
is reviewed by at least one, but typically more, members of the
\astropy community, providing feedback and allowing contributors to
improve their skill is developing software without the need for their
institutions to provide dedicated teaching resources. Thus, the
\astropy project does not only build the tools needed to perform
productive astronomical research in an era of increasingly large and
complex datasets, it also helps to prepare the current and the next
generation of researchers with the knowledge to adequately use those
tools.

>>>>

\section{Conclusion}
\label{sec:conclusion}
% Renamed and edited by Adrian PW

The development of the \astropypkg package and cultivation of the \astropy
ecosystem is still maintaining significant growth while improving stability,
breadth, and reliability.
As the \astropypkg core package becomes more mature, several subpackages have
reached stability with a rich set of features that help astronomers worldwide to
perform many daily tasks such as planning observations, analyzing data or
simulation results, and writing publications.
The strong emphasis that the \astropy project puts on reliability and code
correctness helps users to trust the calculations performed with \astropypkg and
to publish reproducible results.
At the same time, the \astropy ecosystem and core package are growing: new
functionality is still being contributed, and new affiliated packages are being
developed to support more specialized needs.

The \astropy project is also spreading awareness of best practices in
community-driven software development.
This is important as most practicing astronomers were not explicitly taught
computer science and software development, despite the fact that a major
fraction of nearly every astronomer's workload today is related to software use
and development.
The \astropypkg package leads by example, showing all interested astronomers how
modern tools like \texttt{git} version control or continuous integration can
increase the quality, accessibility, and discoverability of astronomical
software without overly complicating the development cycle.
Within \astropy, all submitted code is reviewed by at least one, but typically
more, members of the \astropy community, who provide feedback to contributors
to help improve their skills.
As a community, we follow an explicit code of conduct \citep{ape8} and treat all
contributors and users with respect, provide a harassment-free environment, and
encourage and welcome new contributions from all.
Thus, while the \astropy project provides and develops software and tools
essential to modern astronomical research, it also helps to prepare the current
and next generation of researchers with the knowledge to adequately use,
develop, and contribute to those tools within conscientious and welcoming
community.
